### 2018-08-21 Sections/foreword.tex
Cite van meter

\dropcap{Q}{uantum} technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, musicians, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have -- the creation of the global quantum internet \cite{bib:Kimble2008}. We expect the answer to that question will look very different to what emerged from the classical internet.

>>>>

\dropcap{Q}{uantum} technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, musicians, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have -- the creation of the global quantum internet \cite{bib:van2014quantum, bib:Kimble2008}. We expect the answer to that question will look very different to what emerged from the classical internet.
